Causal Forest Approach for Site-specific Input Management via On-farm Precision Experimentation

### 2022-03-19 Codes/PrepareResults.rmd

vis_RMSE_y_eonr <-
  res_y_test %>%
  .[sim %in% sim_no & Method %in% c("RF", "BRF", "CNN") & Model == "aabbyytt"] %>%
  ggplot() +
    geom_point(aes(x = rmse_y, y = rmse_optN, shape = Method, fill = factor(sim)), size = 2) +
    scale_shape_manual(values = c(21, 23, 25)) +
    ylim(NA, 95) +
    labs(y = " RMSE of EONR Estimation (kg/ha)") +
    labs(x = " RMSE of Yield Prediction (kg/ha)") +
    theme_dist +
    labs(fill="Simulation Round", shape="Method") +
    guides(fill = guide_legend(override.aes=list(shape=21))) +
    # guides(fill=guide_legend(nrow=2, byrow=TRUE)) +
    # guides(shape=guide_legend(nrow=2, byrow=TRUE)) +
    theme(legend.position="bottom", legend.box="vertical", legend.margin=margin()) +
    labs(fill="Simulation Round", shape="Method") 
```

@@

#/*--------------------------------*/
#' ## Yield prediction
#/*--------------------------------*/ 
report_table_y_low_high <-
  Simres_low_high %>%
  .[type == "test" & Method %in% c("RF", "BRF")] %>%
  .[, .(rmse_y = mean(rmse_y)), by = .(Degree, Method, Model)] %>%
  .[, rmse_y := format(round(rmse_y, 1), nsmall = 1)] %>%
  dcast(Degree + Model ~ Method, value.var = "rmse_y") %>%
  .[, CF_base := "-"] %>%
  mutate(
    across(
      everything(),
      as.character
    )
  ) %>%
  as_grouped_data(, groups = c("Degree")) %>%
  flextable(.) %>%
  set_header_labels(values = list(
    Degree = "Error Size",
    Model = "Model",
    RF = "RF",
    BRF = "BRF",
    CF_base = "CF-base"
  )) %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  #- change the borders just for consistency with other figures -#
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  autofit() %>%
  width(j = 1, width = 0.8)
```

>>>>

vis_RMSE_y_eonr <-
  res_y_test %>%
  .[sim %in% sim_no & Method %in% c("RF", "BRF", "CNN") & Model == "aabbyytt"] %>%
  ggplot() +
  geom_point(aes(x = rmse_y, y = rmse_optN, shape = Method, fill = factor(sim)), size = 2) +
  scale_shape_manual(values = c(21, 23, 25)) +
  ylim(NA, 95) +
  labs(y = " RMSE of EONR Estimation (kg/ha)") +
  labs(x = " RMSE of Yield Prediction (kg/ha)") +
  theme_dist +
  labs(fill = "Simulation Round", shape = "Method") +
  guides(fill = guide_legend(override.aes = list(shape = 21))) +
  # guides(fill=guide_legend(nrow=2, byrow=TRUE)) +
  # guides(shape=guide_legend(nrow=2, byrow=TRUE)) +
  theme(legend.position = "bottom", legend.box = "vertical", legend.margin = margin()) +
  labs(fill = "Simulation Round", shape = "Method")
```

@@

# /*--------------------------------*/
#' ## Yield prediction
#/*--------------------------------*/ 
report_table_y_low_high <-
  Simres_low_high %>%
  .[type == "test" & Method %in% c("RF", "BRF")] %>%
  .[, .(rmse_y = mean(rmse_y)), by = .(Degree, Method, Model)] %>%
  .[, rmse_y := format(round(rmse_y, 1), nsmall = 1)] %>%
  dcast(Degree + Model ~ Method, value.var = "rmse_y") %>%
  .[, CF_base := "-"] %>%
  mutate(
    across(
      everything(),
      as.character
    )
  ) %>%
  as_grouped_data(, groups = c("Degree")) %>%
  flextable(.) %>%
  set_header_labels(values = list(
    Degree = "Error Size",
    Model = "Model",
    RF = "RF",
    BRF = "BRF",
    CF_base = "CF-base"
  )) %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  #- change the borders just for consistency with other figures -#
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  autofit() %>%
  width(j = 1, width = 0.8)
```

### 2022-03-19 Writing/appendix.rmd

```{r report-table-optN-low, tab.cap = "Table I.1: Mean RMSE (kg/ha) estimation and profit-deficit ($/ha) by ML method and modeling scenario on low yield disturbance datasets"}
report_table_optN_low
```

```{r report-table-y-low, tab.cap = "Table I.2: Mean RMSE of yield prediction (kg/ha) by ML method and modeling scenario on training datasets on low yield disturbance datasets"}
report_table_y_low
```

@@

```{r report-table-optN-low, tab.cap = "Table I.3: Mean RMSE (kg/ha) estimation and profit-deficit ($/ha) by ML method and modeling scenario on low yield disturbance datasets"}
report_table_optN_high
```

```{r report-table-y-low, tab.cap = "Table I.4: Mean RMSE of yield prediction (kg/ha) by ML method and modeling scenario on training datasets on low yield disturbance datasets"}
report_table_y_high
```

>>>>

```{r report-table-optN-low, tab.cap = "Table I.1: Mean RMSE (kg/ha) estimation and profit-deficit ($/ha) by ML method and modeling scenario on low and high degree of yield disturbance datasets"}
table_optN_prep_low_high
```

@@

```{r report-table-optN-low, tab.cap = "Table I.2: Mean RMSE of yield prediction (kg/ha) by ML method and modeling scenario on low and high degree of yield disturbance datasets"}
report_table_y_low_high
```
